---
title: "Analysing and visualizing the Datasets using R MarkDown"
author: ' By Akhila Kvns'
date: "16 January, 2017"
output:
  word_document: default
  pdf_document: default
  html_document: default
Output: html_document
---
#Introduction

This is an introduction to R Markdown. Here i am going to visualize the following datasets:

* ChickWeight

* Iris

##Description

**1. CHICKWEIGHT **

The ChickWeight data frame has 250 rows and 4 columns fro an experiment on the effect of diet on early growth of chicks.


```{r}
library(datasets)
data(ChickWeight)
summary(ChickWeight)
head(ChickWeight)
```

**2. IRIS **

Theiris dataset gives the measurements in centimeters of the variables sepal length and width and petal length and width, respectively, for 50 flowers from each of 3 species of iris. The species are Iris setosa, versicolor, and virginica.


```{r}
library(datasets)
data(iris)
summary(iris)
head(iris)
```

Now we are using the following functions on the datsets.

1. plot()

2. hist()

###Plot()

* ChickWeight
```{r}
plot(ChickWeight$weight , ChickWeight$Diet)
plot(ChickWeight$weight , ChickWeight$Chick)
```

* Iris

```{r}
plot(iris$Sepal.Length, iris$Sepal.Width)
plot(iris$Petal.Length, iris$Petal.Width)
```

###Hist()

* ChickWeight

```{r}
hist(ChickWeight$weight)
hist(ChickWeight$Time)
```

* Iris

```{r}
iris_obs <- iris$Species == "setosa"
setosa <- iris[iris_obs,]
hist(setosa$Sepal.Length , breaks=10)
hist(setosa$Petal.Length, breaks=5)
```

##Bar plot()

Here we are using bar plot to plot our datsets

* ChickWeight

```{r}
barplot(ChickWeight$weight, ChickWeight$Time)
```

* Iris

```{r}
barplot(iris$Sepal.Length, iris$Petal.Length)
```

##Box plot()

Here we use box plot to plot both the datasets.

1. ChickWeight

```{r}
boxplot(ChickWeight$Chick, ChickWeight$weight)
```

2. Iris

```{r}
boxplot(iris$Sepal.Width, iris$Petal.Width)
```

##Pairs()

For finding the relation between two entities of a dataset, we use pairs() function.

* ChickWeight

```{r}
pairs(ChickWeight)
```

* Iris

```{r}
pairs(iris)
```

Now, we use the par() function which is used for listing all the parameters and plotting multiple plots.

##Par() for ChickWeight

```{r}
par(mfrow=c(1,2))
plot(ChickWeight$weight, ChickWeight$Time)
plot(ChickWeight$Time, ChickWeight$Chick)
```

##Par() for Iris

```{r}
par(mfcol=c(2,2))
plot(iris$Sepal.Length, iris$Sepal.Width)
plot(iris$Petal.Length, iris$Petal.Width)
plot(iris$Sepal.Length, iris$Petal.Length)
plot(iris$Sepal.Width, iris$Petal.Width)


```

#Using ggplots

For plotting the ggplot we use qplot() function.

1. ChickWeight

```{r}
library(ggplot2)
qplot(weight, Time , data=ChickWeight)
qplot(weight, Time, data=ChickWeight, color=Chick)
qplot(weight, Time, data=ChickWeight, geom= c("point", "smooth"))
```

2. Iris

```{r}
library(ggplot2)
qplot(Sepal.Length, Sepal.Width, data=iris)
qplot(Petal.Length, Petal.Width, data=iris, color=Species)
qplot(Sepal.Length, Petal.Width, data=iris, geom= c("point", "smooth"))
```

##Using histograms

We have to specify only one variable for plotting a histogram in ggplot.

* ChickWeight

```{r}
qplot(weight, data=ChickWeight, fill=Diet, binwidth=10)
```

* Iris

```{r}
qplot(Sepal.Length, data=iris, fill=Species, binwidth=20)
```

###Facets

We create separate plots using facets.

* ChickWeight

```{r}
qplot(weight, Diet, data=ChickWeight, facets= .~Time, binwidth=30)
```

* Iris

```{r}
qplot(Sepal.Length, Petal.Length, data=iris, facets=Sepal.Width~.)
```

##Density smooth

* ChickWeight

```{r}
qplot(weight, data=ChickWeight, geom="density", color=Time)
```

* Iris

```{r}
qplot(Sepal.Width, data=iris, geom="density", color=Species)
```

##Scatter plots with shape

* Scatter plot for ChickWeight.

```{r}
qplot(weight,Time, data=ChickWeight, shape=Chick)
```

In order to find out the missing values, we use the following:

```{r}
library(Amelia)
library(mlbench)
missmap(ChickWeight, legend=TRUE, col=c("blue","yellow"))
```


* Scatter plot for the dataset iris.

```{r}
qplot(Petal.Length, Petal.Width, data=iris, shape=Species)
```


##Fitting linear models

 1. ChickWeight
 
```{r}
Data1fit <- lm(weight ~ Time + Chick, data=ChickWeight)
plot(Data1fit)
```

2. Iris

```{r}
Data2fit <- lm(Sepal.Length + Petal.Length ~ Sepal.Width + Petal.Width, data=iris)
plot(Data2fit)
```



